Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-21 ms.tex
wrote a bunch of to do notes to self in fig captions.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
{\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top Left:} An example read pair subtraction with an overlay of the apertures.
{\it Top Right:} An example read pair subtraction after reduction steps with an overlay of the apertures.
{\it Top Left:} The time series constructed from raw dark frames.
{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied.
The most important step in reducing the noise is the 1/f, which is reduced by side reference pixels. 
}\label{fig:longDarkPhot}
\end{figure*}

@@

The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

@@

There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
\begin{enumerate}[noitemsep]
	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
\end{enumerate}
The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^- \approx 930 $DN.
This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm. {\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should correct to 20 groups)}}
This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.}\label{fig:OTISRectBacksub}
\end{figure}

@@

\begin{figure*}
\gridline{\fig{ap_labels_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular aperture subtraction box.
}\label{fig:GLtSeriesBacksub}
\end{figure*}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
{\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
\textcolor{red}{Things to try: 1) put in a panel w/ background subtraction and maybe one with median of all ref pixels within an amplifier 2) check if there's any fringing 3) compare scatter in spectrum to photon + read noise}
}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top Left:} An example read pair subtraction with an overlay of the apertures.
{\it Top Right:} An example read pair subtraction after reduction steps with an overlay of the apertures.
{\it Top Left:} The time series constructed from raw dark frames.
{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied.
The most important step in reducing the noise is the 1/f, which is reduced by side reference pixels. 
\textcolor{red}{Thing to try: show 3 panels w/ last one using row by row and column by column}
}\label{fig:longDarkPhot}
\end{figure*}

@@

The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
\textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}

@@

There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
\begin{enumerate}[noitemsep]
	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
\end{enumerate}
The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^- \approx 930 $DN.
This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm. {\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should corrected to 20 groups)}}
This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.
\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
\end{figure}

@@

\begin{figure*}
\gridline{\fig{ap_labels_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular background subtraction box.
\textcolor{red}{To do: understand why the ratio of the two box time series has a larger standard deviation than in Figure \ref{fig:GLtSeries}. Is it just the poor SN from a small background box? Also, separately, compare two different detectors.}
}\label{fig:GLtSeriesBacksub}
\end{figure*}
